\documentclass[12pt]{article}

\usepackage[ruled,vlined,linesnumbered]{algorithm2e}

\usepackage{times}
\usepackage{anysize}
\marginsize{2cm}{2cm}{2cm}{3cm}
%\onehalfspace
%\doublespace
\setlength{\parindent}{0.8cm}
%\setlength{\parskip}{0.2\baselineskip}
%\setlength{\topmargin}{2cm}
%\setlength{\textheight}{25cm}
%\setlength{\textwidth}{14cm}
%\setlength{\oddsidemargin}{2cm}
%\setlength{\evensidemargin}{2cm}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{url}


\linespread{1}

\lhead{Data-and-Model Driven Reasoning} \rhead{R. Stern and B. Juba}
\cfoot{\thepage} 
%\cfoot{} 
\pagenumbering{arabic}
%\pagenumbering{Roman}

\begin{document}

\section*{Biographical Sketch}

\subsection*{Senior Personnel: Roni Stern (PI)}
\paragraph{Professional Preparation}
\ \\
\begin{tabular}{lll}
{\em Undergraduate institution:}& & \\
Bar Ilan University &Computer Science&B.Sc., 2001\\
 & & \\
{\em Graduate institutions:}& & \\
Bar Ilan University &Computer Science&M.Sc., 2001\\
Ben Gurion University of the Negev&Information Systems Engineering&Ph.D., 2012\\
 & & \\
{\em Postdoctoral Institutions:}& & \\
Ben Gurion University of the Negev&Information Systems Engineering &2011--2012\\
Harvard University&Computer Science&2012--2013
\end{tabular}
\paragraph{Appointments}
\ \\
\begin{tabular}{lll}
Ben Gurion University of the Negev&
Software and Inf. Sys. Engineering &\\
&Lecturer& 2013--2016 \\
&Senior Lecturer& 2017--present
\end{tabular}
\sloppy{
  
\paragraph{Publications - five most related}
\begin{itemize}
  \item  R.~Stern and B.~Juba.
    \newblock Efficient, Safe, and Probably Approximately Complete Learning of 
              Action Models.
    \newblock In {\em Proceedings of the 26th International Joint Conference on
              Artificial Intelligence, IJCAI 2017}, pages 4405--4411, Melbourne,
              Australia, 2017. 
    \newblock Available at     \url{http://www.cse.wustl.edu/~bjuba/papers/pac-planning-ijcai.pdf}

  \item A.~Elmishali, R.~Stern, and M.~Kalech
    \newblock Data-Augmented Software Diagnosis.
    \newblock In {\em Proceedings of the 28th AAAI Conference on Innovative Applications of Artificial
              Intelligence (IAAI),} pages 4003--4009, Pheonix, AZ, USA, 2016.
    \newblock Available at
      \url{http://www.aaai.org/ocs/index.php/IAAI/IAAI16/paper/download/12279/12320}
  
  \item R.~Stern, A.~Felner, R.~Holte 
    \newblock Search-Aware Conditions for Probably Approximately Correct Heuristic Search.
    \newblock In {\em Proceedings of the Symposium on Combinatorial Search ({SoCS}),} 2012.
    \newblock Avaliable at 
      \url{http://www.aaai.org/ocs/index.php/SOCS/SOCS12/paper/view/5374}.

  \item T.~Zamir, R.~Stern, M.~Kalech.
    \newblock Using Model-Based Diagnosis to Improve Software Testing.
    \newblock In {\em Proceedings of the 28th AAAI Conference on Artificial Intelligence, pages 1135--1141, 2014 , Québec City, Canada}
    \newblock Electronic version: \url{https://www.aaai.org/ocs/index.php/AAAI/AAAI14/paper/view/8582}

  \item R.~Stern, M.~Kalech, S.~Rogov, A.~Feldman.
  \newblock How many diagnoses do we need?
  \newblock In Artificial Intelligence journal (AIJ), 
    volume 248, pages 26--45, 2017
\newblock Available at     \url{http://www.sciencedirect.com/science/article/pii/S0004370217300309?via%3Dihub}
\end{itemize}
\paragraph{Publications - five other}
\begin{itemize}
 \item G.~Sharon, R.~Stern, A.~Felner, N.~Sturtevant. 
    \newblock Conflict-based search for optimal multi-agent pathfinding.
    \newblock In Artificial Intelligence journal (AIJ),
    volume 219, pages 40--66, 2015. 
    \newblock Available at \sloppy{\url{http://www.sciencedirect.com/science/article/pii/S0004370214001386?via%3Dihub}}
    
 \item 	R.~Stern, A.~Felner, J.~van den Berg, R.~Puzis, R.~Shah, K.~Goldberg.
    \newblock Potential-based bounded-cost search and Anytime Non-Parametric A*.
    \newblock In Artificial Intelligence journal (AIJ),
    volume 214, pages 1--25, 2015. 
    \newblock Available at \url{http://www.sciencedirect.com/science/article/pii/S0004370214000551?via%3Dihub}


 \item R.~Stern, S.~Kiesel, R.~Puzis, A.~Felner, W.~Ruml.
    \newblock Max Is More than Min: Solving Maximization Problems with Heuristic Search.
    \newblock In {\em Proceedings of the 24th International Joint Conference on
              Artificial Intelligence, IJCAI 2015}, pages 4324--4330,  Buenos Aires, Argentina, 2015
    \newblock Available at \url{http://www.ijcai.org/Proceedings/15/Papers/615.pdf}.

  \item A.~Metodi, R.~Stern, M.~Kalech, and M.~Codish.
  \newblock A Novel SAT-Based Approach to Model Based Diagnosis.
    \newblock In J. Artif. Intell. Res. (JAIR), volume 51, pages 377--411, 2014. 
    \newblock Available at \url{http://jair.org/media/4503/live-4503-8245-jair.pdf}.

  
  
    \item R.~Valenzano, S.~{Jabbari Arfaee}, J.~Thayer, R.~Stern, and N.~Sturtevant.
    \newblock Using Alternative Suboptimality Bounds in Heuristic Search.
    \newblock In {\em Proceedings of the 23rd International Conference on Automated Planning and Scheduling ({ICAPS})}, pages 123--132, Rome, Italy, Rome, 2013.

\end{itemize}
\paragraph{Synergistic Activities}
\begin{enumerate}
\item The PI has supervised 6 graduate students (4 male and 2 females) and is currently supervising 11 graduate students (13 male, 3 females). 
\item The PI has developed a graduate course on theories and applications of collaborating machines. 
\item The PI is currently serving as the president of the International Symposium on Combinatorial Search (SoCS), and has served 
the program chair for the International Symposium on the Principles of Diagnosis (DX), 2016, and for SoCS 2015. 
\item The PI has served on conference program committees, including AAMAS (2012,2014-2016,2018), AAAI (2012-2018), IJCAI (2011,2013,2015 -- senior PC,2017), SoCS (2012-2017), DX (2012-2017), and ECAI (2014,2016). 
The PI has reviewed for AIJ, JAIR, JAAMAS, AMAI, and JASIST.
\item The PI has served as a reviewer for the ISF and for the Czech science foundation. 
\end{enumerate}
}
\end{document}