\documentclass[12pt]{article}

\usepackage[ruled,vlined,linesnumbered]{algorithm2e}

\usepackage{times}
\usepackage{anysize}
\marginsize{2cm}{2cm}{2cm}{3cm}
%\onehalfspace
%\doublespace
\setlength{\parindent}{0.8cm}
%\setlength{\parskip}{0.2\baselineskip}
%\setlength{\topmargin}{2cm}
%\setlength{\textheight}{25cm}
%\setlength{\textwidth}{14cm}
%\setlength{\oddsidemargin}{2cm}
%\setlength{\evensidemargin}{2cm}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{url}


\linespread{1}

\lhead{Data-and-Model Driven Reasoning} \rhead{R. Stern and B. Juba}
\cfoot{\thepage} 
%\cfoot{} 
\pagenumbering{arabic}
%\pagenumbering{Roman}

\begin{document}
\section*{Budget Justification}
\paragraph{Senior Personnel -- line A}
One month's support each year to facilitate work by the PI on the project during
the summer.

\paragraph{Other Personnel -- line B}
Support for one graduate student to work on the project full-time during the first year at the standard student salary at Washington  University, and for two graduate students in years two and three.

\paragraph{Fringe Benefits -- line C}
Standard fringe benefits rate at Washington University for the PI for one
summer month each year.

\paragraph{Travel -- line E}
Funding to support attendance at conferences to facilitate dissemination of the
work, specifically a domestic conference trips (eg., to AAAI) during each year for each member of the team, \$5000 total in year one and \$7000 total in years two and three (line E1); and to support one international conference trip for each member of the team at approximately \$3750 each (line E2). The location of international conference travel will depend on the location of the conferences deemed most appropriate to the results obtained in that year.

Funds are also requested to support an annual two-week face-to-face research meeting between the US and Israeli teams during the summer to facilitate the collaboration. We estimate the costs of these meetings to similarly be \$2000 for lodging, \$1400 for airfare, \$700 for meals per non-local participant, for a total annual cost of \$12300 for the three visiting members (line E2).

\paragraph{Publication costs -- line G}
Funds for three additional pages total per year, typically \$275 per page (line G2).

\paragraph{Indirect costs -- line I}
F\&A at the current standard 52.5\% rate for Washington University each year.

\end{document}