\documentclass[12pt]{article}

\usepackage[ruled,vlined,linesnumbered]{algorithm2e}

\usepackage{times}
\usepackage{anysize}
\marginsize{2cm}{2cm}{2cm}{3cm}
%\onehalfspace
%\doublespace
\setlength{\parindent}{0.8cm}
%\setlength{\parskip}{0.2\baselineskip}
%\setlength{\topmargin}{2cm}
%\setlength{\textheight}{25cm}
%\setlength{\textwidth}{14cm}
%\setlength{\oddsidemargin}{2cm}
%\setlength{\evensidemargin}{2cm}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{url}


\linespread{1}

\lhead{Data-and-Model Driven Reasoning} \rhead{R. Stern and B. Juba}
\cfoot{\thepage} 
%\cfoot{} 
\pagenumbering{arabic}
%\pagenumbering{Roman}

\begin{document}
\section*{Budget Justification}
Following NSF-BSF regulations, the budget justified in this document is only for the budget requested for the Israeli PI. 

\paragraph{Salaries}
The main bulk of the requested funding is for funding graduate students that will participate in this research as part of their Ph.D. studies. PI Stern is currently mentoring a group of 11 M.Sc. students and 5 Ph.D students, where some of the students are co-supervised with other other faculty members. Several of these students are expected to work on topics related to the proposed research, if won. In addition, we intend to join new graduate students to take part in both theoretical progress as well as the experimental part of the research. 
Thus, we request 20,000 USD each year to partially support Ph.D. students working on the proposed research, and an additional 7500 USD in the final year to fund a scientific programmer to implement the developed algorithm in a way that will enable broader dissemination of our results. 

\paragraph{Equipment}
An important part of the proposed research, which will be led by the Israeli PI, is to perform experimental studies that show the developed model-and-data driven approach is competitive and outperforms the current state of the art planning and diagnosis algorithms. Thus, running experiments is a crucial part of the proposed research. Therefore, we request 7,500 USD in the first year and second years to fund three personal computers, two for the participating graduate students and one for PI Stern, as well as computer peripherals (screens, docking stations, etc.), software (Office, Matlab, etc.), and miscellaneous. We do not request funding for a large server as PI Stern already has funding for such server as part of the startup grant he received from BGU.

\paragraph{Supplies}
We request 250-200 USD per year to fund photocopies and editing services.

\paragraph{Travel}
We plan to have two meetings a year on this research project, beyond the bi-weekly Skype calls. One meeting will take place in Israel and the other in the US. The duration of each meeting will be between one and two weeks, depending on research progress. In this budget request we ask for 7,000 USD per year to uphold this meetings and allow the Israeli PI and his student to participate in these meetings, which will take place either in a conference or at WUSTL. 


\end{document}




