\documentclass[12pt]{article}

\usepackage[ruled,vlined,linesnumbered]{algorithm2e}

\usepackage{times}
\usepackage{anysize}
\marginsize{2cm}{2cm}{2cm}{3cm}
%\onehalfspace
%\doublespace
\setlength{\parindent}{0.8cm}
%\setlength{\parskip}{0.2\baselineskip}
%\setlength{\topmargin}{2cm}
%\setlength{\textheight}{25cm}
%\setlength{\textwidth}{14cm}
%\setlength{\oddsidemargin}{2cm}
%\setlength{\evensidemargin}{2cm}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{url}


\linespread{1}

\lhead{Data-and-Model Driven Reasoning} \rhead{R. Stern and B. Juba}
\cfoot{\thepage} 
%\cfoot{} 
\pagenumbering{arabic}
%\pagenumbering{Roman}

\begin{document}
\section*{Work Schedule}


[[Roni: copy and paste from 2016 BSF. Must be modified to 3 years, and to better reflect our work]]


\paragraph{Explanatory Notes}
{\bf Year 1.} In the first year both groups will focus on the planning task, and specifically on the setting in
which a complete model of the relevant world is given along with past observations. PI Juba`s group
will focus on the theoretical analysis of this setting, including seeking reasonable assumptions to take
that will allow effective learning of the heuristic model as well as sound analysis. PI Stern`s group will
develop and evaluate empirical PAC search algorithms and conditions on a range of domains.

{\bf Year 2.} In the second year, we will still focus on planning but we will relax the assumption that a
complete model is given. PI Juba`s group will focus on how to learn PAC semantic rules that are valid
for planning. Meanwhile, PI Stern`s group will develop planning algorithms that makes use of PAC
semantic rules for planning, by finding plans that are likely to be correct.


{\bf Year 3.} In the third year, we will focus on the diagnosis problem, again starting from the easier case in
which a complete model is available and the given observation are needed to improve diagnostic
accuracy. PI Juba`s group will work on the theoretical analysis of this setting, including analyzing the
number and type of observations needed. PI Stern`s group will explore algorithms that learn a fault
prediction model from the observations in Boolean circuits and in software systems.


{\bf Year 4.} In the last year we will focus on the diagnosis problem, but where a complete model is not
give. PI Juba`s group will work on how to learn PAC semantic rules for diagnosis, and what need to be
assumed, while PI Stern will d


\end{document}














